---

title: "Untitled"
author: "AL"
date: "2025-05-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, message = FALSE, warning = FALSE}
library(tidyverse)
library(RSQLite)
library(dbplyr)
library(scales)
library(slider)
library(furrr)
library(broom)
library(lmtest)
library(rlang)
db_path <- "/home/shared/data/tidy_finance.sqlite"
```



```{r}
tidy_finance <- dbConnect(
  SQLite(),
  db_path,
  extended_types = TRUE
)

```

```{r}
dbListTables(tidy_finance)
```


```{r}
crsp_daily_raw <- tbl(tidy_finance, "crsp_daily")
```


```{r}
crsp_monthly <- tbl(tidy_finance, "crsp_monthly") |>
 # select(permno, date, industry, ret_excess) |>
  collect()
```

### Column Explanations

| Column        | Type     | Meaning |
|---------------|----------|--------|
| `permno`      | `<dbl>`  | **Permanent Number** — unique stock identifier assigned by CRSP. |
| `date`        | `<date>` | **Date** — monthly date for the return data (e.g., end-of-month). |
| `ret`         | `<dbl>`  | **Return** — raw return for the stock over the month (includes dividends). |
| `shrout`      | `<dbl>`  | **Shares Outstanding** — number of shares (in thousands) at month-end. |
| `prc`         | `<dbl>`  | **Price** — closing price at month-end (usually signed to indicate bid/ask). |
| `primaryexch` | `<chr>`  | **Primary Exchange** — exchange where the stock is primarily traded (e.g., NYSE, NASDAQ). |
| `siccd`       | `<int>`  | **SIC Code** — Standard Industrial Classification code identifying industry. |
| `mktcap`      | `<dbl>`  | **Market Capitalization** — computed as `prc * shrout` (in dollars). |
| `mktcap_lag`  | `<dbl>`  | **Lagged Market Cap** — market cap from the previous period (for predictive sorting). |
| `exchange`    | `<chr>`  | **Exchange Code or Label** — similar to `primaryexch`, may differ by format. |
| `industry`    | `<chr>`  | **Industry Category** — human-readable industry classification. |
| `ret_excess`  | `<dbl>`  | **Excess Return** — return minus risk-free rate (monthly excess return). |
| `gvkey`       | `<chr>`  | **Global Company Key** — unique firm identifier from Compustat (joins with fundamentals). |

---

### Summary

This is a cleaned and enriched monthly CRSP dataset with stock returns, pricing info, market cap, and industry mappings. It’s commonly used for asset pricing research and factor model estimation.

Would you like a code snippet to explore or summarize


```{r}
names_tbl <- tbl(tidy_finance, "stksecurityinfohist") %>%
  select(permno, securitynm) %>%
  distinct()

crsp_named <- tbl(tidy_finance, "crsp_monthly") %>%
  inner_join(names_tbl, by = "permno") %>%
  select(permno, date, securitynm, ret_excess) %>%
  collect()


```



```{r}
names_tbl <- tbl(tidy_finance, "stksecurityinfohist") %>%
  select(permno, securitynm, securitytype, ticker, tradingsymbol) %>%
  distinct()

crsp_daily_named <- tbl(tidy_finance, "crsp_daily") %>%
  left_join(names_tbl, by = "permno") %>%
  collect()


crsp_monthly_named <- tbl(tidy_finance, "crsp_monthly") %>%
  left_join(names_tbl, by = "permno") %>%
  collect()


```


```{r}
write.table(crsp_daily_named, "crsp_daily_named.txt", sep = "\t", row.names = FALSE, quote = FALSE)
write.table(crsp_monthly_named, "crsp_monthly_named.txt", sep = "\t", row.names = FALSE, quote = FALSE)
```

























